### 2019-04-30 dantzig_selector/report/3_theorems_and_proofs.tex
Set & correct simulation variables
Kronecker product identity proof
Correct vectorize convention

We apply DS to find \m {\hat {\V {g}}}, setting
\Disp {
\NC \gamma = \NC \R {2 \log N_h} \NR[+]
}

Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp {
\NC \V {d} = \NC \hat {\V {g}} -\V {g} \NR[+]
}
%
And call
\startitemize [1]
\item \m {\Mc {A}} be the largest \m {s} position of \m {g}.
\item \m {\Mc {B}} be the largest \m {s} position of \m {d_{T\SB {N_h} -\Mc {A}}}.
\item \m {\Mc {C} =T \RB {N_h} -\Mc {A}}, i.e., the complementary index set of \m {\Mc {A}}.
\stopitemize

@@

\Result
{Lemma (Tentative)}
{
Suppose \m {0 \leq \f \leq 2\pi k /N_H}, \m {k =0, \dots, N_H-1}.
Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
%
\Disp {
\NC R
\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
}
}

We show the lemma, which is the key to bounding the sparsity of \m {h}.
Recall the identity for Dirichlet kernel
%
\Disp {
\NC D \SB {\f'}
:= \NC \Nm { \sum_{n=0}^{N_H-1} \Mr {e}^{i n \f'} } \NR
\NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
\NC \quad 0 \leq \NC  \f' \leq \pi \NR
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp {
\NC \sin x = \NC x -\F {x^3}{6} + \Mc {O} \SB {x^5}, \quad x \ll 1 \NR
}
%
Actually it can be shown that we have a inequality
%
\Disp {
\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}, \NR[+]
\NC -\pi \leq \NC x \leq \pi \NR
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp {
\NC \Nm {D \SB {\f'} }
= \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}}
\quad 0 \leq \f' \leq \pi. \NR
}

Particularly, for arbitrary \m {\f}, find \m {k} so that
\Disp {
\NC \eta := \NC \f -\F {2\pi k}{N_H}, \NR[+]
\NC \Nm {\eta}
\leq \NC \F {2\pi}{N_H}. \NR
}
%
Then observe
\Disp {
\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {k}
=\NC \F {1}{N_H} D \RB {\f -\F {2 \pi k} {N_H}} \NR
}
So we need only bound
\Disp {
\NC R\SB {\eta}
:=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB { \eta +\F {2 \pi n_H} {N_H} } \NR
}
By the approximation of rectangle to integral,
\Disp {
\NC R\SB {\eta} -\F {2\pi} {N_H}
\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D\SB {\f'}} d \f' \NR
}
Bound \m {D} by above technique, meanwhile we notice \m {\f' <24}.
\Disp {
\NC R\SB {\f}
\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{\RB {24 -\f'^2} \f'} d \f'
+\F {2\pi} {N_H} \NR
\NC = \NC \F {1}{\pi} \log \F {2\pi N_H}{L}
-\F {1}{N_H} \log \F {4\pi^2 -24} {L^2/N_H^2 -24}
+\F {2\pi} {N_H}
}
Notice the argument of log in the second term \m {<1}, and we drop that.
Also drop \m {2\pi /N_H} since it is small.
Furthermore the \m {2\pi} factor in log can be dropped too.
\Disp {
\NC R\SB {\f}
\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
}

\Result
{Lemma (Tentative)}
{
Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)}, and linear array response \m {\V {a}} defined as in ().
Let \m {\V {g}} be defined as above.
Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
%
\Disp {
\NC R
\leq \NC \F {L}{\pi^2} \RB { \log \F {N_H}{L} }^2 \NR
}
}

@@

\Result
{Definition}
{
For \m {\Mc {T}, \Mc {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
%
\Disp {
\NC \Nm {\IP {P_{\Mc {T}} h, P_{\Mc {T}'} h'}}
\leq \NC \tau_{s, s'} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
}
}

@@

\Result
{Proposition}
{
Let \m {\V {g}} and \m {\V {d}} be defined as above.
Then
%
\Disp {
\NC \VNm {\V {d}_{\Mc {C}}} _1
\leq \NC \VNm {\V {d}_{\Mc {A}}} _1 +2\VNm {\V {g}_{\Mc {C}}} _1 \NR
}
}

@@

\Result
{Lemma}
{
Let \m {\V {z}} and \m {\M {P}} be defined as above.
Then
%
\Disp {
\NC \Nm {\IP { \V {z}, \M {P} \DB {:, n_g} }}
\leq \NC  2 \R {\log N_h},
\quad n_g =1, \dots, N_h. \NR
}
%
with overwhelming probability.
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in ().
%
\Disp {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h},
\quad n_g =1, \dots, N_h. \NR
}
}

To show this, by definition
%
\Disp {
\NC \IP { \V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y} }
= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y} } \NR
\NC = \NC \IP { \M {P} \V {d}, \M {P} \DB {:,n_y} } \NR
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in () with respect to \m {\d_s}.
%
\Disp {
\NC \VNm {\V {d}_{\Mc {AB}}} _2
\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\Mc {A} \Mc {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
}
%
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} be defined as above.
Then
%
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC \VNm {\V {d}_{\Mc {A} \Mc {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\Mc {C}}} _1^2 \NR
}
%
}

>>>>

We apply DS to find \m {\hat {\V {g}}}, setting
\Disp {
\NC \g = \NC \R {2 \log N_h} \NR[+]
}

Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
\Disp {
\NC \V {d} = \NC \hat {\V {g}} -\V {g} \NR[+]
}
And call
\startitemize [1]
\item \m {\Mc {A}} be the largest \m {s} position of \m {g}.
\item \m {\Mc {B}} be the largest \m {s} position of \m {d_{T\SB {N_h} -\Mc {A}}}.
\item \m {\Mc {C} =T \RB {N_h} -\Mc {A}}, i.e., the complementary index set of \m {\Mc {A}}.
\stopitemize

@@

\Result
{Lemma (Tentative)}
{
Suppose \m {0 \leq \f \leq 2\pi k /N_H}, \m {k =0, \dots, N_H-1}.
Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
\Disp {
\NC R
\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
}
}

We show the lemma, which is the key to bounding the sparsity of \m {h}.
Recall the identity for Dirichlet kernel
\Disp {
\NC D \SB {\f'}
:= \NC \Nm { \sum_{n=0}^{N_H-1} \Mr {e}^{i n \f'} } \NR
\NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
\NC \quad 0 \leq \NC  \f' \leq \pi \NR
}
And recall the Taylor expansion of sin for the first two terms with respect to zero
\Disp {
\NC \sin x = \NC x -\F {x^3}{6} + \Mc {O} \SB {x^5}, \quad x \ll 1 \NR
}
Actually it can be shown that we have a inequality
\Disp {
\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}, \NR[+]
\NC -\pi \leq \NC x \leq \pi \NR
}
Applying the above inequality to the denominator and bounding the nominator by 1, we have
\Disp {
\NC \Nm {D \SB {\f'} }
= \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}}
\quad 0 \leq \f' \leq \pi. \NR
}

Particularly, for arbitrary \m {\f}, find \m {k} by
\Disp {
\NC \eta := \NC \f \quad \rm{mod}\; (2\pi) \NR[+]
\NC k := \NC \F {N_H} {2\pi} (\f -\eta) \NR[+]
}
Then observe
\Disp {
\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {k}
=\NC \F {1}{N_H} D \RB {\f -\F {2 \pi k} {N_H}} \NR
}
So we need only bound
\Disp {
\NC R\SB {\eta}
:=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB { \eta +\F {2 \pi n_H} {N_H} } \NR
}
By the approximation of rectangle to integral,
\Disp {
\NC R\SB {\eta} -\F {2\pi} {N_H}
\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D\SB {\f'}} d \f' \NR
}
Bound \m {D} by above technique, meanwhile we notice \m {\f' <24}.
\Disp {
\NC R\SB {\f}
\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{\RB {24 -\f'^2} \f'} d \f'
+\F {2\pi} {N_H} \NR
\NC = \NC \F {1}{\pi} \log \F {2\pi N_H}{L}
-\F {1}{N_H} \log \F {4\pi^2 -24} {L^2/N_H^2 -24}
+\F {2\pi} {N_H}
}
Notice the argument of log in the second term \m {<1}, and we drop that.
Also drop \m {2\pi /N_H} since it is small.
Furthermore the \m {2\pi} factor in log can be dropped too.
\Disp {
\NC R\SB {\f}
\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
}

\Result
{Lemma (Tentative)}
{
Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)}, and linear array response \m {\V {a}} defined as in ().
Let \m {\V {g}} be defined as above.
Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
\Disp {
\NC R
\leq \NC \F {L}{\pi^2} \RB { \log \F {N_H}{L} }^2 \NR
}
}

@@

\Result
{Definition}
{
For \m {\Mc {T}, \Mc {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
\Disp {
\NC \Nm {\IP {P_{\Mc {T}} h, P_{\Mc {T}'} h'}}
\leq \NC \tau_{s, s'} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
}
}

@@

\Result
{Proposition}
{
Let \m {\V {g}} and \m {\V {d}} be defined as above.
Then
\Disp {
\NC \VNm {\V {d}_{\Mc {C}}} _1
\leq \NC \VNm {\V {d}_{\Mc {A}}} _1 +2\VNm {\V {g}_{\Mc {C}}} _1 \NR
}
}

@@

\Result
{Lemma}
{
Let \m {\V {z}} and \m {\M {P}} be defined as above.
Then
\Disp {
\NC \Nm {\IP { \V {z}, \M {P} \DB {:, n_g} }}
\leq \NC  2 \R {\log N_h},
\quad n_g =1, \dots, N_h. \NR
}
with overwhelming probability.
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in ().
\Disp {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h},
\quad n_g =1, \dots, N_h. \NR
}
}

To show this, by definition
\Disp {
\NC \IP { \V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y} }
= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y} } \NR
\NC = \NC \IP { \M {P} \V {d}, \M {P} \DB {:,n_y} } \NR
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in () with respect to \m {\d_s}.
\Disp {
\NC \VNm {\V {d}_{\Mc {AB}}} _2
\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\Mc {A} \Mc {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
}
}

@@

\Result
{Lemma}
{
Let \m {\V {d}} be defined as above.
Then
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC \VNm {\V {d}_{\Mc {A} \Mc {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\Mc {C}}} _1^2 \NR
}
}
